Normalization Performance Analysis for the Paired MSK Data Sets

### 2021-02-25 MSK_Data_Analysis.Rmd
Added Readme

  p.density.neg.nnz.freq <- ggplot(neg.corr, aes(x=corr, colour=control, linetype=control)) +
    geom_freqpoly(binwidth=.05, alpha=.8, size=.9) +
    theme_classic() +
    xlim(0, 1) +
    # scale_linetype_manual(values=c("twodash", "solid", "solid", "solid"))+
    scale_color_manual(values=c('#e7298a','#1B9E77','#D95F02', '#7570B3')) + # First colors from rcolorbrewer set "Dark2"
    theme(legend.position=c(0.9,0.86), 
          legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.5))) +
    ylab("Frequency") +
    xlab("Marginal correlation") #+ ggtitle("Positive correlation among negative controls")
  print(p.density.neg.nnz.freq)

@@

  p.cutoffs <-
    plot_grid(p.RC.conf1,
              p.RC.conf2 + labs(x="Mean", y=element_blank()),
              p.RC.conf3 + labs(x="Mean", y=element_blank()),
              p.meanvar.conf1,
              p.meanvar.conf2 + labs(x="Mean", y=element_blank()),
              p.meanvar.conf3 + labs(x="Mean", y=element_blank()),
              p.result.DANA.1,
              p.result.DANA.2 + labs(y=element_blank()),
              p.result.DANA.3 + labs(y=element_blank()),
              align="hv",
              labels=c("a","b","c"))
  print(p.cutoffs)

>>>>

  p.density.neg.nnz.freq <- ggplot(neg.corr, aes(x=corr, colour=control, linetype=control)) +
    geom_freqpoly(binwidth=.05, alpha=.8, size=.9) +
    theme_classic() +
    xlim(0, 1) +
    # scale_linetype_manual(values=c("twodash", "solid", "solid", "solid"))+
    scale_color_manual(values=c('#e7298a','#1B9E77','#D95F02', '#7570B3')) + # First colors from rcolorbrewer set "Dark2"
    theme(legend.position=c(0.9,0.86), 
          legend.title=element_blank(),
          legend.background=element_rect(fill=alpha('white', 0.5))) +
    theme(legend.key.width = unit(1.25,"cm")) +
    ylab("Frequency") +
    xlab("Marginal correlation") #+ ggtitle("Positive correlation among negative controls")
  print(p.density.neg.nnz.freq)

@@

  p.cutoffs <-
    plot_grid(p.RC.conf2,
              p.RC.conf1 + labs(x="Mean", y=element_blank()),
              p.RC.conf3 + labs(x="Mean", y=element_blank()),
              p.meanvar.conf2,
              p.meanvar.conf1 + labs(x="Mean", y=element_blank()),
              p.meanvar.conf3 + labs(x="Mean", y=element_blank()),
              p.result.DANA.2,
              p.result.DANA.1 + labs(y=element_blank()),
              p.result.DANA.3 + labs(y=element_blank()),
              align="hv",
              labels=c("a","b","c"))
  print(p.cutoffs)
